\documentclass[10pt]{article} 
\usepackage{jjz_resume} 

\title{Jessica J. Zhang} 
\date{\today} 
\setemail{\href{mailto:jessicajzhang03@gmail.com}{jessicajzhang03@gmail.com}} 
\setwebsite{\href{https://jessicajzhang03.github.io}{jessicajzhang03.github.io}}
\setgithub{jessicajzhang03} 

\begin{document}
\sffamily
\pagestyle{empty}
\maketitle 
\begin{center}
\printinfo{\emailsymbol}{\email}
\printinfo{\websitesymbol}{\website} 
% \printinfo{\githubsymbol}{\github}
\end{center}

\color{body}
\section{Education} 
\cvitem{Proof School}{August 2017--present}{
Current GPA 5.00 out of 5.00. 
Completed coursework includes Graph Theory 2, Algebraic Number Theory, Point-Set Topology, and Noncommutative Ring Theory. 
Currently taking Differential Geometry. 
}

\section{Experience}
\cvitem{MIT PRIMES-USA researcher}{January--December 2020}{
With Dr.~Zhenkun Li, fully classified tight contact structures on solid tori. 
Gave a talk titled ``Fundamentals of contact geometry'' to mathematically advanced high school students as part of the Math ROCs conference. 
}

\cvitem{MORPH participant}{June--August 2020}{
Participated in a reading group as part of the Mathematics Online Reading Program for High schoolers. 
Learned functional analysis, with a special focus on probability theory and distributions.
}

\cvitem{Joint Mathematics Meetings Undergraduate Poster Presenter}{January 2020, 2021}{
Invited to the Joint Mathematics Meetings as an undergraduate presenter as a result of research performed at PROMYS in 2019 and at MIT PRIMES in 2020. 
}

\cvitem{PROMYS program participant}{June--August 2018, 2019}{
Participated in PROMYS, a six-week mathematics summer program. 
Completed advanced seminars in graph theory and analytic number theory. 
Researched and presented on the relationship between graphs and matroids and their Jacobians, under the guidance of Professor Matthew Baker. 
Invited back in 2020 as a junior counselor. 
}

\section{Honors}
\cvitem{Regeneron Science Talent Search Finalist}{January 2021}{
Named a top 40 finalist in the 2021 Regeneron Science Talent Search; final placement will be announced in March.
}

\cvitem{S.-T.~Yau High School Awards USA Bronze Medalist}{November 2020}{
Won a bronze medal in mathematics research for research on the classification of contact structures.
}

\section{Papers and publications}
\paper{Classification of tight contact structures on a solid torus}{\href{https://arxiv.org/abs/2006.16461}{\texttt{arXiv:2006.16461}}}{With Z. Li (submitted)}

\paper{Exponents of Jacobians of graphs and regular matroids}{\href{https://arxiv.org/abs/1910.06442}{\texttt{arXiv:1910.06442}}}{With H. Lheem, D. Li, and C. J. Quines}

\section{Skills}
\vspace{-2mm}
\noindent{\normalfont\LaTeX}, Asymptote, Python, Flask, HTML/CSS

\lastupdated
\end{document}
